TITLE

### 2021-10-18 paper.tex
update

\documentclass[twocolumn]{aastex63}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
%\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p\delta^{ij}\right)=0,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}}\left(\frac{\partial\gamma}{\partial t} + \frac{1}{c}\partial_{j} U^{j}\right),\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density, \
the momentum densities, and the reduced energy density, respectively. \
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas. \
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density. \
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
%\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=0,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
the momentum densities, and the reduced energy density, respectively.\
The reduced energy density is defined by subtracting the rest mass energy density of gas\
from the total energy density of gas.\
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
$p_{\text{gas}}$ is the gas pressure.\
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.
